Combinatorial Proofs and Decomposition Theorems for First-order Logic

### 2021-01-12 main.tex
tiny changes

We define a congruence relation on formulas by the following equations:
\begin{equation*}
  \begin{array}{cc}
    A \vlan B \fequ B \vlan A & A \vlor B \fequ B \vlor A \\
    (A \vlan B) \vlan C \fequ A \vlan (B \vlan C) &
    (A \vlor B) \vlor C \fequ A \vlor (B \vlor C) \\
    \forall x . \forall y . A \fequ \forall y . \forall x . A &
    \exists x . \exists y . A \fequ \exists y . \exists x . A \\
    \forall x . (A \vlor B) \fequ (\forall x . A) \vlor B &
    \exists x . (A \vlan B) \fequ (\exists x . A) \vlan B
  \end{array}
\end{equation*}
where $x \notin fv(B)$ in the last two equations.

\begin{thm}
  Let $A,B$ be rectified formulas. Then
  $$
  A\fequ B \iff \graphof A =\graphof B
  $$
\end{thm}

>>>>

We define a congruence relation $\fequ$ on formulas by the following equations:
\begin{equation*}
  \begin{array}{cc}
    A \vlan B \fequ B \vlan A & A \vlor B \fequ B \vlor A \\
    (A \vlan B) \vlan C \fequ A \vlan (B \vlan C) &
    (A \vlor B) \vlor C \fequ A \vlor (B \vlor C) \\
    \forall x . \forall y . A \fequ \forall y . \forall x . A &
    \exists x . \exists y . A \fequ \exists y . \exists x . A \\
    \forall x . (A \vlor B) \fequ (\forall x . A) \vlor B &
    \exists x . (A \vlan B) \fequ (\exists x . A) \vlan B
  \end{array}
\end{equation*}
where $x \notin fv(B)$ in the last two equations.
Two formulas $A$ and $B$ are \bfit{equivalent} if $A \fequ B$. The following
theorem shows that the set of fographs can been seen as the quotient
$\FORM / \fequ$.
\begin{thm}
  Let $A,B$ be rectified formulas. Then
  $$
  A\fequ B \iff \graphof A =\graphof B
  $$
\end{thm}
